\documentclass[10pt, letterpaper]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{url}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}

\urlstyle{same}
\begin{document}

\begin{center}
\textbf{\Large MAX BALDIVIEZO}\\
\end{center}

\begin{center}
\textbf{Machine Learning} | \textbf{Python} | \textbf{SQL} | \textbf{TensorFlow} | \textbf{AWS} | \textbf{SageMaker} | \textbf{Matplotlib}
\end{center}

\vspace{0.2cm}

\begin{flushleft}
\textbf{CONTACT INFORMATION}
\end{flushleft}

\begin{itemize}[noitemsep]
\item[] GitHub: \url{https://github.com/Maxbm19}
\item[] Email: maxabaldiviezo@gmail.com
\item[] LinkedIn: \url{http://linkedin.com/in/maxbaldiviezo}
\end{itemize}

\vspace{0.2cm}

\begin{flushleft}
\textbf{SUMMARY}
\end{flushleft}

Experienced Data Scientist with a strong background in segmentation, predictive analysis, and deploying machine learning models on AWS SageMaker. Proficient in Python, Jupyter notebooks, and familiar with various ML frameworks. Excellent problem-solving skills and a proven ability to collaborate in fast-paced environments.

\vspace{0.2cm}

\begin{flushleft}
\textbf{WORK EXPERIENCE}
\end{flushleft}

\textbf{Data Scientist | Tigo (Telecommunications Company) | 2023-Present}

\begin{itemize}[noitemsep]
\item Developed and deployed machine learning models for churn prediction and upsell prediction for prepaid clients using AWS SageMaker.
\item Improved the upsell model that was previously managed by a consulting company, significantly enhancing its performance.
\item Created the churn prediction model from scratch, optimizing it through hyperparameter tuning.
\item Automated the deployment and maintenance of models using CI/CD pipelines, ensuring efficient and scalable deployment.
\item Collaborated with cross-functional teams to integrate machine learning models into business processes, driving data-driven decision-making.
\item Leveraged AWS SageMaker for model development, deployment, and hyperparameter tuning, ensuring robust and scalable solutions.
\end{itemize}

\vspace{0.2cm}

\textbf{Data Analyst | ProcessMaker  | 2022-2023}

\begin{itemize}[noitemsep]
\item Built a system of dynamic and automated reports/dashboards using G-Suite tools, providing real-time monitoring of marketing and sales performance metrics from the ground up.
\item Developed lead scoring models and dynamic dashboards to aid sales teams in prioritizing leads, boosting new sales pipelines.
\item Conducted client profit and loss estimations to optimize operational efficiency.
\item Effectively communicated insights with colleagues, particularly those at the headquarters in the United States.
\item Collaborated seamlessly with IT and business departments to identify data requirements and build data pipelines from various sources, such as CRM systems, financial reports, Google Analytics, and Amazon Web Services.
\end{itemize}

\vspace{0.2cm}

\begin{flushleft}
\textbf{EDUCATION}
\end{flushleft}

\textbf{Advanced Data Analytics Certification | Universidad Privada de Bolivia | 2022-2023}

\begin{itemize}[noitemsep]
\item[] Completed an advanced certification program in Data Analytics, including courses in statistical modeling, machine learning, deep learning, and data visualization.
\item[] Worked on several data-driven projects, applying various tools and techniques to analyze and visualize data.
\end{itemize}

\vspace{0.2cm}

\textbf{Bachelor's degree in Electrical Engineering | Universidad Autónoma Gabriel René Moreno | 2018-2022}

\begin{itemize}[noitemsep]
\item[] Worked as a teaching assistant while completing the degree, teaching numerical methods and fluid mechanics to students in Electrical, Electronic, Mechanical, and Electromechanical Engineering.
\item[] Utilized Excel and Python to teach numerical methods and solve problems through software.
\item[] Managed students' progress and provided feedback on their assignments and projects.
\end{itemize}

\end{document}

